---
title: "Basic Linear Regression Implementation"
author: "Sebastian Masinde Omkar"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
### Introduction
This package was developed as part of a LAB assignment at Link\"oping Universtiy. The package fits a Linear Regression Model using Ordinary Least Squares and QR decompostion method. So far, only former gives t-values and p-values while the latter gives estimates of beta and residuals and variances of the beta estimates. The functions:
- linreg: Linear Regression function by OLS
- linreg_QR: Linear Regression function by QR decomposition. 

### Formula:

```{r formula1, eval = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
linreg(formula, data)
```

```{r formula2, eval = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
linreg_QR(formula, data)
```


### Implementation Examples:

```{r imp1, eval = FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
data(faithful)

linreg(eruptions ~ waiting, data= faithful)
```

```{r imp2, eval=FALSE}
data(iris)

linreg_QR(Petal.Length ~ Species, data = iris)
```

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
